---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# funfurther

<!-- badges: start -->
<!-- badges: end -->

The goal of funfurther is to add some new features to existing `strsplit` function.

## Installation

You can install the released version of funfurther from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("devtools")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Hazel233/Useful-R-Packages")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(funfurther)
x <- c("3D/MON&SUN")
strsplit(x, "", type = "before")
```

## Assignment2-STAT545B

My first R Package repository on GitHub starting from STAT545B. The following parts are some explanation for this assignment!

### E1.1 The explaination of the development

`library(devtools)` is used to prepare for the tools. Then,
`create_package("~/Desktop/funfurther")` and `use_git()` are introduced
for create folder in user’s desktop and prepare for git operation
seperately. `use_r("strsplit")` can save the function in a `.R` file.
Finally use `load_all()` to make the function available for
experimentation. To be sure that all the moving parts of the foofactors
package still work, apply `check()` to do this. And use
`use_mit_license("Hazel Hao")` to set license for one’s work.

### E1.2 Tests

`usethis` and `testthat` are used especially to test those new
functions.

### E1.3 Documentation of the R package

1.  `document()` is used to update my documentation. The only object is
    set to be exported for use.
2.  Other tasks have been done and can be found in corresponding files.

